hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2024-12-04 inst/manuscript/paper.Rmd
add catfish example

```{r, eval=FALSE}
smallmouth <- matrix(NA, 10, 2) |> tibble()
colnames(smallmouth) <- c("hours", "temp_F")
smallmouth$hours <- c(52, 54, 70, 78, 90, 98, 150, 167, 238, 234)
smallmouth$temp_F <- c(77, 75, 71, 70, 67, 65, 60, 59, 55, 55)

@@

plot(smallmouth$days~smallmouth$temp_C)

smb_mod <- fit_model(smallmouth,
                     temp = smallmouth$temp_C,
                     days = smallmouth$hours)

>>>>

```{r, eval=FALSE}
#### temp regime
set.seed(1234)
temps <- sort(rnorm(n =30, mean = 20, sd = 1), decreasing = TRUE)

smallmouth <- matrix(NA, 10, 2) |> tibble()
colnames(smallmouth) <- c("hours", "temp_F")
smallmouth$hours <- c(52, 54, 70, 78, 90, 98, 150, 167, 238, 234)
smallmouth$temp_F <- c(77, 75, 71, 70, 67, 65, 60, 59, 55, 55)

@@

plot(smallmouth$hours~smallmouth$temp_C)

smb_mod <- fit_model(smallmouth,
                     temp = smallmouth$temp_C,
                     days = smallmouth$days,
                     species = "smb",
                     dev.type = "hatch")

### catfish example from Small and Bates 2001
### Effect of Low-Temperature Incubation of Channel Catfish Ictalarus punctatus
### Eggs on Development, Survival, and Growth
### Journal of the World Aquaculture Society
catfish <- matrix(NA, 3, 2) |> tibble()
colnames(catfish) <- c("days", "temp_C")
catfish$days <- c(16,21,26)
catfish$temp_C <- c(22,10,7)

cat_mod <- fit_model(catfish,
                     temp = catfish$temp_C,
                     days = catfish$days,
                     species = "catfish",
                     dev.type = "hatch")
